Implementing \& Evaluating Space Efficient Algorithms for Detecting Large Neighbourhoods in Graph Streams

### 2020-02-28 paper/src/paper.tex
l0 algorithms

@@

>>>>

\DontPrintSemicolon % Don't print semicolons in algorithm environment

@@

\newpage
\begin{algorithm}[H]
\caption{Single $l_0$-Sampler for vector}
\SetKwInOut{Require}{require}
\Require{Vector $\textbf{a}=(a_1,\dots,a_n)$}
$j=1$.\\
$\textbf{a}_j=\textbf{a}$.\\
\While{true}{
	H=new hash function.\\
	$a_{j+1}=\pmb0$.\\
	$j=j+1$.\\
	\tcp{Sampling}
	\For{$i\in[1,n]$}{
		$h=H(i)$.\\
		\lIf{$h\leq\frac{n^3}{2^j}$}{$a_{j+1,i}=a_{j,i}$}
		\lElse{$a_{j+1,i}=0$}
	}
	$\textbf{a}_{j}=\textbf{a}_{j+1}$
	\;
	\tcp{Attempt Recover}
	$w_1:=\sum a_{j,i}$.\\
	$w_2:=\sum ia_{j,i}$.\\
	\;
	\If{$w_2\equiv0$}{\Return$\mathtt{FAIL}$\tcp*{$a_j\equiv\pmb0$}}
	\If{$w_1\equiv1$}{\Return$w_2$\tcp*{Index of non-zero value}}
}
\end{algorithm}
Hash functions should be k-wise independent and map from $n$ to $n^3$ where $n$ is the number of vertices in the graph (\ie length of vector since it is from a graph matrix).

\begin{algorithm}[H]
\caption{Single $l_0$-Sampler for a stream}
\SetKwInOut{Require}{require}
\Require{Stream $\textbf{s}=\{s_1,\dots,s_n\}$ with $n$ known, Hash Function $H$}
sampled=\{\}.\\
\For{$i\in[1,n\}$}{
$h=H(i)$.\\
\lIf{$h\leq\frac{n^3}{2^1}$}{sampled.append($s_i$)}
}
$j=1$.\\
\While{sampled.size()$>1$}{
  $j=j+1$.\\
  new\_sample=\{\}.\\
  \For{$i\in[1,\text{sampled.size()}]$}{
    $h=H(i)$.\tcp*{Consider changing hash function}
    \lIf{$h\leq\frac{n^3}{2^j}$}{new\_sample.append(sampled[i])}
  }
  sampled=new\_sample.
}
\lIf{sampled.size()$\equiv1$}{\Return{Success,sampled[0]}}
\Return{Fail,NULL}
\end{algorithm}

\begin{algorithm}[h]
\caption{$m$ Parallel $l_0$-Samplers for a stream}
\SetKwInOut{Require}{require}
\Require{Stream $\textbf{s}=\{s_1,\dots,s_n\}$ with $n$ known, Hash Functions $\textbf{H}=\{H_1,\dots,H_m\}$}
output=\{\}.\\
sampled=\{\{\}\}.\\
\For{$i\in[1,n]$}{
\tcp{Single pass of stream}
  \For{$j\in[1,m]$}{
    $h=H_j(i)$.\\
    \lIf{$h\leq\frac{n^3}{2^1}$}{sampled[j].append($s_i$)}
  }
}
\For{$j\in[1,m]$}{
  $k=1$.\\
  \While{sampled[j].size()$>1$}{
    $k=k+1$.\\
    new\_sample=\{\}.\\
    \For{$i\in[1,\text{sampled[j].size()}]$}{
      $h=H_j(i)$.\tcp*{Consider changing hash function}
      \lIf{$h\leq\frac{n^3}{2^k}$}{new\_sample[j].append(sampled[i])}
    }
    sampled[j]=new\_sample.
  }
  \lIf{sampled[j].size()$\equiv1$}{output.append(sampled[j][0])}
}
\Return{output}
\end{algorithm}
